\chapter{Data}

\textit{Introduce how there is a lot of nba data and how the nba is shifting towards analytics.  Talk about the sources and collection and storage.}

\section{Data Sources}
There are a multitude of resources for NBA data including basketball reference, the official NBA website and others.

There is a ton of information available from each basketball game.  The models will use data from the 2013-14, 2014-15 and 2015-2016 season.  The 2016-17 season is used as a testing set.  Data collected includes game logs, season stats for teams and players.  The game logs include the total statistics from a game for all different basketball stats and the timestamp of every thing happening tagged by the player.  This leads to a lot of information for the games.

\section{Data Collection}



Due to several teams relocating and changing their names over the previous seasons, this led to challenges in scraping the data.

Using the Beautiful Soup library \cite{beautifulsoup}, the data was scraped.

\section{Data Storage}
Once the data was collected, it was stored using MongoDB which is a NoSQL database.  This allows for ease of manipulation.

\begin{listing}
\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4]{js}
{
    '_id': '201310300DAL', 
    'date': 30/10/13 
    'season': 2014, 
    'result': 1, 
    'home': {
        'team': 'DAL', 
        'pts': 118, 
        'fg': 44, 
        'fga': 77, 
        'fg_pct': 0.571, 
        'fg3': 11, 
        'fg3a': 24, 
        'fg3_pct': 0.458, 
        'ft': 19, 
        'fta': 24, 
        'ft_pct': 0.792, 
        'orb': 7, 
        'trb': 42, 
        'ast': 31, 
        'stl': 7, 
        'blk': 2, 
        'tov': 20, 
        'pf': 22,
    }, 
    'away': {
        'team': 'ATL', 
        'pts': 109, 
        'fg': 37, 
        'fga': 76, 
        'fg_pct': 0.487, 
        'fg3': 8, 
        'fg3a': 24, 
        'fg3_pct': 0.333, 
        'ft': 27, 
        'fta': 35, 
        'ft_pct': 0.771, 
        'orb': 5, 
        'trb': 33, 
        'ast': 27, 
        'stl': 16, 
        'blk': 5, 
        'tov': 17, 
        'pf': 20
    }
    'bet': {
        'home': 1.2
        'away': 2.3
    }
}

\end{minted}
\caption{Game Log Between dallas and atlanta} 
\label{json-example}
\end{listing}