\chapter{Data}\label{chapter:data}

\textit{Talk about how much data there is, }

The NBA has been shifting towards data analytics in the past few years.  The evolution began in baseball with the book Moneyball.  For this project, the data used will be game logs for players and teams in the past few seasons

\textit{Introduce how there is a lot of NBA data and how the NBA is shifting towards analytics.  Talk about the sources and collection and storage.}

\section{Data Sources}
The data for the National Basketball Association is publicly available on a number of different platforms.  For this project, Basketball-Reference \citep{basketball_reference} was used.  Historical betting odds were also required.  They were obtained from BetExplorer \citep{betting_odds}.  Unfortunately, historical prop betting on basketball was not available anywhere.  Thus, the betting analysis will be limited only to scorelines.

\section{Data Collection}

Using the Beautiful Soup library \cite{beautifulsoup}, the data was scraped.

\section{Betting Odds}

In addition to predicting the winner of a game, betting odds allow another use case for the model.
A description of different betting odds. \cite{betting_odds}

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Bet Type} & \textbf{Description} \\ \hline
Money Line & Bet on the winner of the game. \\ \hline
Spread & Bet on score difference between two teams. \\ \hline
Over/Under & Bet on the total number of points scored \\ \hline
\end{tabular}
\caption{Betting Types}
\label{my-label}
\end{table}
