\chapter{Introduction}

\section{Motivation}
Fantasy sports mix the real world with virtual games to provide an exiting environment to try out prediction algorithms on real world data.  Fantasy sports have seen exponential growth since their inception and are now an important part of the sports industry.  Currently more than 29 million North Americans participate in a fantasy sports league \cite{fantasy_football_effects}.  Each season, fantasy sports players must draft their team and select a weekly or daily lineup for their matches.  The team selection introduces the problem of selecting the team formations that have a maximum value over the course of the season.

\section{Objectives}
The main objectives are:

\begin{enumerate}
	
	\item \textbf{Predict NBA Games}
	
	The team a player is facing will have a big impact on their performance.  Thus, it is important to predict the outcome of an NBA game.  This will be done using machine learning classification techniques that predict whether the home team wins.  
	
	\item \textbf{Predict Player Performance}
	
	In fantasy basketball, players' real-life statistics are used and matched against other fantasy teams to determine a winner.  Thus, coming up with an accurate player prediction model is essential for the team formation problem.
	
	\item \textbf{Optimise Team Selection}
	
	The team formation problem may be tackled once a player model has been designed.  In fantasy basketball, teams are chosen via a draft.  Players may also trade or claim a player from free agency (a player who was not drafted).  Once a team is selected, a fantasy basketball player must, on a daily basis, select the starting lineup from their team which will achieve the greatest performance.
	
\end{enumerate}

\section{Report Structure}
Chapter 2 will provide the background necessary for the report.  Chapter \ref{chapter:data} provides an insight into the data collected and used for the project.  Chapters \ref{chapter:team_model} and \ref{chapter:player_model} present the models and implementation.  Chapters \ref{chapter:betting} and \ref{chapter:fantasy} evaluate the models. Chapter \ref{chapter:conclusion} is the conclusion.