\chapter{Sports Betting}\label{chapter:betting}

Using the model developed in the previous section, we can take a look at the betting markets.  Betting odds used in betting markets are simply a probability of a team winning.  So we will use the probabilities generated from our model and compare them to the betting odds to determine where we should place our money.

\textit{Look at Pope and Peel (1989) and Dixon and Pope (1006)}

Using historical odds for the 2014-15, 2015-16 and 2016-17 seasons, we are able to determine the betting proficiency of the model.  We are using model (4.52), with $\xi = 0.062$ and $\omega=0.17$ at each time point to estimate the results.  Once probabilities for matches are obtained, we can compare with the bookies' odds to determine which match should be bet and calculating the profit.

\section{Betting Strategy}
In order to maximize profits, a number of betting strategies were implemented.

The parameters obtained to maximize the prediction accuracy might not accurately reflect the probabilities outputted by the model for the betting market.  Thus, to obtain new values of $\xi$ and $\omega$ the following equation will be used.

\begin{equation}\label{eq:score}
S(\xi) = \sum_{k=1}^{N}(\delta_k^H\log p_k^H + \delta_k^A \log p_k^A)
\end{equation}

where, $\delta_k^H = 1$ if match $k$ was a home win and $\delta_k^H=0$ otherwise and vice versa for $\delta_k^A$.  As shown in Figure 2, the function is maximised at $\xi = 0.102$.  Equation (\ref{eq:score}) is also used to maximise the value of $\omega$ as shown in Figure 3.  The value is maximised at $\omega = 33.2$.